---
title: "Wealth and Life Expectancy"
author: "Braden Burt"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
editor_options: 
  chunk_output_type: inline
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(dplyr)
library(gapminder)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
dat <- gapminder %>%
  filter(country != "Kuwait") %>%
  group_by(continent, year) %>%
  summarise(newmean = weighted.mean(gdpPercap, pop), sumofpop = sum(pop/100000))
```

## Background

I learned a lot about how to plot during this Case Study.  It was really helpful to learn the basics of making graphs in R, but I also found that this assignment presented the chance to experiment with different functions in R until I found the one to make the desired effect.  As well as plotting, I feel that now I understand more of how to sort through and see the dataset I'm working with.

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

```

## Data Visualization

```{r plot_data, echo=FALSE}
# Use this R-Chunk to plot & visualize your data!
ggplot(data = gapminder %>% filter(country != "Kuwait"), mapping = aes(x = lifeExp, y = gdpPercap, color = continent, size = pop/100000)) + 
  geom_point() + 
  theme_bw() + 
  scale_y_continuous(trans = "sqrt") +
  facet_wrap(~year, ncol = 12) + 
  labs(size = "Population (100k)", color = "Continent", x = "Life Expectancy",y = "GDP per capita")
ggsave("lifeExp_vs_gdpPercap.png", width = 15)

ggplot(data = gapminder %>% filter(country != "Kuwait")) + 
  geom_line(mapping = aes(x = year, y = gdpPercap, color = continent, group = country, size = 0.1)) +
  geom_point(mapping = aes(x = year, y = gdpPercap, color = continent, group = country, size = pop/100000)) +
  geom_line(data = dat, mapping = aes(x = year, y = newmean)) + 
  geom_point(data = dat, mapping = aes(x = year, y = newmean, size = sumofpop)) +
  theme_bw() + 
  facet_wrap(~continent, ncol = 5) +
  labs(size = "Population (100k)", color = "Continent", x = "Year", y = "GDP per capita")
ggsave("year_vs_gdpPercap.png", width = 15)
```

## Conclusions
